Placeholder for article 3

### 2024-12-28 analysis/paper/paper.qmd
Retouched table start.

proto_tech_WIP <- proto_tech %>%
  tidyr::unite(col='ID', all_of(cols_to_concat_terrace), sep="-", remove=TRUE) %>% 
  rename(CLASS = Class, COREPREPPROD = CorePreparProd, PIECECOMPLETENESS = PieceCompleteness, CORTEX = Cortex, CORTEXLOCATION = CortexLocation, PLATFORMTYPE = PlatformType, PLATFORMCORTEX = PlatformCortex, SCARCOUNT = ScarCount, THICKNESS = Thickness,
        MAXWIDTH = MaxWidth, LENGTH = Length, COREPLATFORM = CorePlatform, MAINFACECORTEX = MainFaceCortex, 
        MAINFACESCARCOUNT = MainFaceScarCount, COREABANDON = CoreAbandon, RETOUCHEDPIECETYOPOLOGY = RetouchedPieceTypology) %>% 
  mutate(RETOUCHEDPIECETYOPOLOGY = case_when(
    RETOUCHEDPIECETYOPOLOGY == "Right truncation on retouched piece" ~ "Truncation",
    RETOUCHEDPIECETYOPOLOGY == "Double backed bladelet" | RETOUCHEDPIECETYOPOLOGY == "Backed bladelet parcial" ~ "Backed bladelet",
    RETOUCHEDPIECETYOPOLOGY == "Dentilhado" ~ "Denticulate",
    RETOUCHEDPIECETYOPOLOGY == "Burin on truncation" ~ "Burin",
    TRUE ~ RETOUCHEDPIECETYOPOLOGY)) %>% 
  dplyr::select(ID, CLASS, COREPREPPROD, PIECECOMPLETENESS, CORTEX, CORTEXLOCATION, PLATFORMTYPE, PLATFORMCORTEX,
                SCARCOUNT, THICKNESS, MAXWIDTH, LENGTH, COREPLATFORM, MAINFACECORTEX, MAINFACESCARCOUNT, COREABANDON,
                RETOUCHEDPIECETYOPOLOGY)

@@

>>>>

proto_tech_WIP <- proto_tech %>%
  tidyr::unite(col='ID', all_of(cols_to_concat_terrace), sep="-", remove=TRUE) %>% 
  rename(CLASS = Class, COREPREPPROD = CorePreparProd, PIECECOMPLETENESS = PieceCompleteness, CORTEX = Cortex, CORTEXLOCATION = CortexLocation, PLATFORMTYPE = PlatformType, PLATFORMCORTEX = PlatformCortex, SCARCOUNT = ScarCount, THICKNESS = Thickness,
        MAXWIDTH = MaxWidth, LENGTH = Length, COREPLATFORM = CorePlatform, MAINFACECORTEX = MainFaceCortex, 
        MAINFACESCARCOUNT = MainFaceScarCount, COREABANDON = CoreAbandon, RETOUCHEDPIECETYPOLOGY = RetouchedPieceTypology) %>% 
  mutate(RETOUCHEDPIECETYPOLOGY = case_when(
    RETOUCHEDPIECETYPOLOGY == "Right truncation on retouched piece" ~ "Truncation",
    RETOUCHEDPIECETYPOLOGY == "Double backed bladelet" | RETOUCHEDPIECETYPOLOGY == "Backed bladelet parcial" ~ "Backed bladelet",
    RETOUCHEDPIECETYPOLOGY == "Dentilhado" ~ "Denticulate",
    RETOUCHEDPIECETYPOLOGY == "Burin on truncation" ~ "Burin",
    TRUE ~ RETOUCHEDPIECETYPOLOGY)) %>% 
  dplyr::select(ID, CLASS, COREPREPPROD, PIECECOMPLETENESS, CORTEX, CORTEXLOCATION, PLATFORMTYPE, PLATFORMCORTEX,
                SCARCOUNT, THICKNESS, MAXWIDTH, LENGTH, COREPLATFORM, MAINFACECORTEX, MAINFACESCARCOUNT, COREABANDON, RETOUCHEDPIECETYPOLOGY)

@@

```{r}
#| label: tool-diversity

proto_retouch <- phase_dataset %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>%
  filter(Level %in% c("4E", "4E/5")) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  dplyr::group_by(RMTYPE)

proto_retouch_tab <- table(proto_retouch$RETOUCHEDPIECETYPOLOGY, proto_retouch$RMTYPE)
proto_retouch_tab <- as.data.frame.matrix(proto_retouch_tab)
